### 2014-06-26 Choosing R3 Relations.tex
started ananalog to prop 5.2

\begin{lem} (Generalized Lemma 5.1) Let i and j be vertices of $\Gamma$.
\begin{enumerate}[(a)]
\item If i = k or j = k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$.
\item If at most one of i,j is connected to k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$
\end{enumerate}
\end{lem}

@@

>>>>

\begin{lem}[Generalized Lemma 5.1]\label{lem:one_connected_to_k} Let i and j be vertices of $\Gamma$.
\begin{enumerate}[(a)]
\item If i = k or j = k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$.
\item If at most one of i,j is connected to k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$
\end{enumerate}
\end{lem}

@@

\begin{lem}[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
\end{lem}

After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.

Beginning with the relations $(R2)$, and following cases a-f from Corollary 2.3 in Barot and Marsh:

\begin{enumerate}[a)]
\item
\begin{enumerate}[i)]
\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item
\begin{align*}
t_it_jt_i &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}\\
&= s_ks_is_js_ks_j^{-1}s_is_k^{-1}\\
&= s_ks_js_is_ks_is_j^{-1}s_k^{-1}\\
&= s_ks_js_ks_is_ks_j^{-1}s_k^{-1}\\
&= s_js_ks_js_is_j^{-1}s_k^{-1}s_j\\
&= s_js_ks_is_k^{-1}s_j\\
&= t_it_jt_i
\end{align*}
\item $$t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item
\begin{align*}
t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}s_js_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}s_ks_js_ks_is_ks_i^{-1}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_js_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}\\
&= e
\end{align*}
\end{enumerate}
\end{enumerate}
